% Vague Writing
A lot of recent studies have shown that most participants experienced a bit of discomfort during the experiment. Some of the stuff recorded was nice, but there were also things that were not specified. The results, and so on, suggest further investigation is needed. Anything can happen in such conditions, and the thing that surprised us most was the variety.

% Exaggerations
The hypothesis was always confirmed in every trial, and the findings absolutely prove the theory. None of the respondents never disagreed, which definitely supports our conclusion.

% Subjectivity
The candidate had a better approach, which was obviously the best among all. The building was beautiful, and the solution seemed perfect. Clearly, the researcher should choose the ideal method, even if it seems wonderful, awful, ugly, or hideous.

% Clichés and Colloquialisms
At the end of the day, the team found a happy medium. In this day and age, researchers have to think outside the box to get through obstacles. The above board approach was a stumbling block for some, but ultimately, when all is said and done, the results were legitimate.

% Fillers
The results were literally very significant, and the method was really too complicated. The conclusion serves to show that so many extremely important factors were involved, which helps to explain the findings.

% Informal and Colloquial Expressions
America has got a big problem with giving good advice. The scholar kind of showed that till now, huge humongous changes have not been observed. The senator said that the government has got to act. The writer got a prize for her work.

% First or second person
I believe that we should reconsider our approach. My results indicate that our data supports the hypothesis. You might think your solution is better, but the researcher performed a regression analysis.
